### 2021-09-22 analysis/fit_models.Rmd
new routine coded up and old removed, each site evaliuated. slight hiccups with the ccdf plotting and need to check with vincent. need to make plots on to the histograms as well as checking out with fits with vincent. unsure on CI's as for any estimate these will be very large, but may be able to make the case of these in the aggregate and get a single CI for many different sites within a given environment.

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
theme_set(
  theme_classic() +
    theme(
      text = element_text(family = "URWHelvetica", size = 8)
    )
)
library(cowplot)
library(dplyr)
library(tibble)
source("analysis/fit_data.R")
```

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
theme_set(
  theme_classic() +
    theme(
      text = element_text(family = "URWHelvetica", size = 8)
    )
)
library(cowplot)
library(dplyr)
library(tibble)
source("analysis/fit_data.R")

```

## Optimising each site

In this document I have fit the collective and individual model to each site. So al the sites have reasonable likelihood values, however in some cases the fits are simply wrong (i.e. they show the probability of sampling a value greater than on equal to $x$ as increasing in the tail). I need to trouble shoot these with Vincent. I also need to get some advice on how to plot the model fits to the histogram of data.

Would be a good idea to knit this as a single document / run in R studio on the laptop.

### BEL

Provides a good fit on the data. All parameters look central and nicely covered.

```{r}

target_site <- "BEL"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 0.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 10, -5.5, -2)
)

# bring results together
bel_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

bel_model_fits

```

### BFI

All parameters look central in the likelihood space and a nice fit is returned.

```{r}

target_site <- "BFI"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 0.6)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 4.5, -8, -2.5)
)

# bring results together
bfi_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

bfi_model_fits

```

### BLO

CCDF plot is not right. Cant go back on its self which indicates there is probably some round off error somewhere throwing things off.

The individual fit isnt great and the Bs paramater is increasing up to the boundry, indicating it can only really take on a straight line / exponential fit. The parameters for the collective model are fairly central which raises questions as to why the fit is misbehaved in the tail.

```{r}

target_site <- "BLO"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-10, 5)
br_bnds <- c(1.0e-10, 5)
as_bnds <- c(1.0e-5, 5)
ar_bnds <- c(1.0e-10, 1.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 105)
as_bnds <- c(1.0e-12, 0.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 12, -8., -2.5)
)

# bring results together
blo_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

blo_model_fits

```

### BUR

Bs and Br go in oposite directions. E.g. Bs approaches 0 whilst Br approaches an every higher number.

Fit looks good.

```{r}

target_site <- "BUR"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 500)
br_bnds <- c(1.0e-6, 500)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 0.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 5.5, -6.5, -2.5)
)

# bring results together
bur_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

bur_model_fits

```

### CAD

The only graph I can get to make sense is one where the collective reduces to the individual. The others show the ccdf going off.

```{r}

target_site <- "CAD"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 100)
br_bnds <- c(1.0e-6, 100)
as_bnds <- c(1.0e-12, 10)
ar_bnds <- c(1.0e-12, 10)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 2)
as_bnds <- c(1.0e-12, 0.8)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 2.5, -5, -1.5)
)

# bring results together
cad_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

cad_model_fits

```

### GIL

Again, the likelihood scores look good but the model fits are doing crazy things at the tail!

```{r}

target_site <- "GIL"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 0.8)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 2.7, -8., -2)
)

# bring results together
gil_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

gil_model_fits

```

### HER

Also has a weird CCDF plot

```{r}

target_site <- "HER"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 100)
br_bnds <- c(1.0e-6, 100)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 2)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 5, -6.5, -1.5)
)

# bring results together
her_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

her_model_fits

```

### HHS

Shit ccdf.

```{r}

target_site <- "HHS"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 50)
br_bnds <- c(1.0e-6, 50)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 6, -6.5, -2.5)
)

# bring results together
hhs_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

hhs_model_fits

```

### HOR

Agin weird behaviour in the tail. Seems to be something to do with the Bs parameter approaching the lower bound. If the lower bound is made closer to zero (just 1e-7) the plot goes mad and the log-likelihood score becomes very large, indicating a round off error or something stupid.

```{r}

target_site <- "HOR"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 4, -9, -2.5)
)

# bring results together
hor_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

hor_model_fits

```

### MAK

Same problem as with the others.

```{r}

target_site <- "MAK"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 5, -6.5, -2.5)
)

# bring results together
mak_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

mak_model_fits

```

### MEL

Slight misbehaviour in the tail creaping up.

```{r}

target_site <- "MEL"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 3.5, -7, -2.5)
)

# bring results together
mel_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

mel_model_fits

```

### MPA

Same problem with the tail.

```{r}

target_site <- "MPA"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 4.5, -7.2, -2.5)
)

# bring results together
mpa_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

mpa_model_fits

```

### ROT

Same problem with the tail.

```{r}

target_site <- "ROT"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 3., -5.5, -2.5)
)

# bring results together
rot_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

rot_model_fits

```

### SAU

No problems here!

```{r}

target_site <- "SAU"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 3.5, -6.5, -2.5)
)

# bring results together
sau_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

sau_model_fits

```

### SOM

Same problem with the tail.

```{r}

target_site <- "SOM"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site) %>%
  filter(foraging_distance < 9) # remove outlier distance

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 3., -5.5, -2.5)
)

# bring results together
som_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

som_model_fits

```

### SRA

Same problem with the tail.

```{r}

target_site <- "SRA"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 4., -7.5, -2.5)
)

# bring results together
sra_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

sra_model_fits

```

### STU

Same problem with the tail. Increasing the bounds for as and ar seems to coerce it towards the better visual fit, despite it not changing what they optimise at. Weird thing is the model is getting close in the region of p but not actually to it.

```{r}

target_site <- "STU"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12,10)
ar_bnds <- c(1.0e-12, 10)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 5.5, -6.5, -1.5)
)

# bring results together
stu_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

stu_model_fits

```

### SWP

Same problem with the tail. Weird P behaviour when we move some of the other parameters around. Looks like it can get a fit that looks very similar with p = 0

```{r}

target_site <- "SWP"

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 15)
br_bnds <- c(1.0e-6, 15)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# subset data for target site
data <- get_data() %>%
  filter(site == target_site)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# run individual model
individual_result <- fit_individual_model_to_data(data, bounds)

# view individual model likelihood space to check bounds look ok
individual_result$llspace

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 2.5, -6, -2.)
)

# bring results together
swp_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

swp_model_fits

```

### YAL

Same problem with the tail.

```{r}

target_site <- "YAL"
